Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Minimum size

@@

@@

\subsection{Minimum clone size}
In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. This implies that

\subsection{Calculating a maintainability score}
In this study we use four metrics to determine maintainability \ref{sec:metrics}. For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We calculate the average deviation as follows:
\begin{equation}\label{eq:type3r}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:type3r}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of

>>>>

To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output. We also created a set of control projects to test the correctness for many edge cases.

@@

We verified the correctness of the resulting refactorings manually. We ran the tool over a large software project and verified over 1.000 applied refactorings.

@@

\subsection{Minimum clone size}
In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, when clones are very small, they may never be able to improve maintainability because the detrimental effect of added volume of the newly created method exceeds the positive effect of removing duplication. Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.

\subsection{Calculating a maintainability score}
In this study we use four metrics to determine maintainability \ref{sec:metrics}. For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We calculate the average deviation as follows:
\begin{equation}\label{eq:type3r}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:type3r}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.
